% !TEX root = /Users/Gela/Desktop/Thesis_latex/thesis.tex

% ordlista

\section*{Dictionary}


\begin{description}
\item [Inlet water:] The water that is pumped into the system from the tank.
\item [Feed water:] The pressurized water stream that i pushed into the feed inlet of the membrane.
\item [Permeate water:]  Purified water stream leaving the membrane as product water.
\item [Reject water:] The brine water leaving the RO-module. The reject water can either be recirculated or rejected through the drain valve.
\item [Drain water:] The water wasted, e.g. water leaving the flow path through the drain valve.
\item [Recirculation loop:] Recirculation path from the reject stream of the RO-module into the feed stream.
\item [Membrane flux:] Flow through the surface of the membrane.
\item [Pressure:]  System pressure, measured in Bar.
\item [Flow:] Water flow in the flow path. Measured in ml/min.
\item [Conductivity:] The electrical conductivity of the water is used to determine the amount of dissolved salts in the fluid. Measured in  (\SI{}{\micro\siemens}/cm).
\item [RO:] Short for Reverse Osmosis
\item [Semi-permeable membrane:] Physical property of the membrane that describes how the membrane is able to let some substances permeate over the mebrane while blocking other substances.
\item [Recovery:] Percentage of feed water that permeate across the membrane into the permeate stream.
\item [DOW:] The DOW chemical company is the manufacturer of the Reverse Osmosis membrane investigated in the thesis.

\end{description}



