\documentclass{LTHthesis}

\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}  %% Comment if you are not using utf8
\usepackage{mathptmx, helvet}
\usepackage{graphicx}
\usepackage{biblatex}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{ntheorem}
\usepackage{latexsym}
\usepackage{framed}
\usepackage{siunitx}
\usepackage{scrextend}
\addtokomafont{labelinglabel}{\sffamily}



\addbibresource{mybib.bib} 

\makeatletter
\newcommand{\mathleft}{\@fleqntrue\@mathmargin40pt}
\newcommand{\mathcenter}{\@fleqnfalse}
\makeatother

\begin{document}
\begin{titlepages}
\author{Angelica Persson and Pontus Lundberg}
\title{Optimization of Reverse Osmosis Performance}
\year{2018}
\month{June}
\TFRT{9999}  %%  You will get the number from the department.
\printer{Media-Tryck}  %% Probably. You may get other information from the department.
\end{titlepages}
\chapter{Abstract}
\include{abstract}
\chapter{Acknowledgements}
\include{acknowledgements}

\tableofcontents

\include{ordlista}

\chapter{Introduction}
\include{introduction}

\chapter{Theory}
\include{theory}


\chapter{Method/Implementation}
\include{method}

\chapter{Results}
\include{results}

\chapter{Discussion}
\include{discussion}

\chapter{Conclusion}
\include{conclusion}

\chapter{Future Prospects}
\include{prospects}

%\printbibliography 
\medskip
\begin{thebibliography}{9}

\bibitem{Singh} 
R, Singh
\textit{Membrane Technology and Engineering for Water Purification(Second edition)},
 Butterworth-Heineman, 2018.
 
 \bibitem{Dow} 
The Dow Chemical Company.
\textit{Dow Water and Process solutions - Levels of Separation of IX, RO, NF, UF}, 
The Dow Chemical Company, 2018.

 \bibitem{Puretech}
 Puretech Industrial Water.
 \textit{What is reverse osmosis}, 
 \textit{https://puretecwater.com/reverse-osmosis/what-is-reverse-osmosis}, 
 2018.

 \bibitem{lambda}
 Panagopoulos H Astrom K J Hagglund T.
 \textit{The Lambda method for Tuning PI Controllers},
 1997.
 
  \bibitem{Z-N}
 Haugen, F.
 \textit{Ziegler-Nichols Closed-Loop Method},
 2010.
 
 \bibitem{PID}
 Goodwin G. Graebe S. Salgado M.
 \textit{Control System design},
 2001.
 
 \bibitem{clamping}
 Haugen, F.
 \textit{Anti-Windup schemes for Proportional Integral and Proportional Resonant Controller}, 
 2010.
 

\end{thebibliography}


\clearpage
\appendix
\chapter{Equipment} 
\label{A}
\input{equipment}



\end{document}


